Hypertension and microbiome

### 2019-05-27 articletwo.Rmd
Cleaning

```{r table beta diversity}
adonis.species$max %>%
    data.table::rbindlist(id = "model_name") %>%
    dplyr::filter(term %in% c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION")) %>%
#    dplyr::select(response, R2, "Pr(>F)") %>%
    mutate(p.value = pub.p(`Pr(>F)`))
```

@@

@@

```{r adonis demo}
data(dune)
data(dune.env)
adonis(dune ~ Management, data=dune.env, permutations=99)$aov.tab
adonis(dune ~ Management, data=dune.env, permutations=99)$coefficients
```

```{r age sex bmi}
lm(MAP ~ BL_AGE + SEX + BMI, data = dset.alpha) %>% summary
```

>>>>

```{r table beta diversity}
adonis.species$max %>%
    data.table::rbindlist(id = "model_name") %>%
    dplyr::filter(term %in% c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION")) %>%
    dplyr::select(response, R2, "Pr(>F)") %>%
    mutate(p.value = pub.p(`Pr(>F)`)) %>%
    kable
```

@@

For magnitude, age, sex, and BMI explain `r round(summary(lm(MAP ~ BL_AGE +
SEX + BMI, data = meta(pseq.genus)))$adj.r.squared * 100, 1)`% of MAP.

@@
